Vestibular Contributions to Spatial Perspective Transformations: From Sensory Inference To Imagined Self-Motion

### 2017-01-28 manuscript.Rmd
word export fixed

lang              : "english"
class             : "man"
output:
     # papaja::apa6_word
     papaja::apa6_pdf
        # pandoc_args:
        # - --filter
        #   pandoc-fignos

@@

```{r preliminary, cache=FALSE, message = FALSE, warning = FALSE}
library(papaja)
# library(pander)
library(ggplot2)
library(dplyr)
library(tidyr)
library(mvtnorm)
# library(ggthemes)
library(cowplot)

@@

```{r head-turn-data, echo=FALSE, fig.cap= "Sensory measurements obtained during a short leftward head turn. The goal is to infer the latent angular velocity and position, based on the noisy measurements.", message=FALSE, warning=FALSE, dpi=100}
dt <- 0.1
motiondata <-  generate_data(T = 2, frequency = 0.5,
                             amplitude = 20,
                             sensor_sd = 2.0)
# plot_trajectories(motiondata = motiondata)

@@

$$\theta_t = \theta_{t-1} + \omega_{t-1} \Delta t + \alpha_{t-1} \frac{1}{2} \Delta t^2$$
$$\omega_{t} = \omega_{t-1} + \alpha_{t-1} \Delta t$$
$$\alpha_t = \alpha_{t-1}$$

@@

$$x_t = f(x_{t-1}, \epsilon)$$
$$y_{t} = g(x_t, \delta)$$
$$\epsilon \sim N(0, \sigma^2_\epsilon)$$
$$\delta \sim N(0, \sigma^2_\delta)$$
<!-- TODO: it is better to start with the generative model, f() and g(), and then implement the state space description -->
where the state variable $x_t$ consists of the position $\theta_t$, velocity $\omega_t$ and acceleration $\alpha_t$, and $y_{t}$ denotes the sensory measurement.
<!-- [^sensormodel]  -->
$\epsilon$ and $\delta$ are zero-mean Gaussian noise terms with variances $\sigma^2_\epsilon$ and $\sigma^2_\delta$. These refer to the process and measurement noise, respectively. The process noise represents the uncertainty in the dependence of the current state on the previous state; under the constant velocity assumption, the process noise must be large enough if the model is to allow for change in velocity due to unmodelled acceleration. Note that the measurement noise is a model of the noise characteristics of the sensor, and not a physical property of the sensor itself. The function $f$ and $g$ represent the process transition function and the measurement function, respectively. 
<!-- In the case of a linear dynamical system, the transition function can be written as: -->
<!-- $$x_t \sim N(Ax_{t-1}), \epsilon^2)$$, -->
<!-- where the matrix $A$ replaces the transition function $f$. -->

@@

```{r 3d-statespace-fits, echo=FALSE, fig.cap="(a) Particle filter with a 3-d state space model for inferring velocity and position during a two-second head turn. (b) The same particle filter with increased process noise.", message=FALSE, warning=FALSE}
cowplot::plot_grid(p_3d_1, p_3d_2, ncol = 2)
```

>>>>

lang              : "english"
class             : "man"
output:
     papaja::apa6_word
     # papaja::apa6_pdf
        # pandoc_args:
        # - --filter
        #   pandoc-fignos

@@

```{r preliminary, message=FALSE, warning=FALSE, cache=FALSE, include=FALSE}
library(papaja)
# library(pander)
library(ggplot2)
library(dplyr)
library(tidyr)
library(mvtnorm)
# library(ggthemes)
library(cowplot)

@@

```{r head-turn-data, fig.cap="Sensory measurements obtained during a short leftward head turn. The goal is to infer the latent angular velocity and position, warning=FALSE, based on the noisy measurements.", message=FALSE, dpi=100, include=FALSE}
dt <- 0.1
motiondata <-  generate_data(T = 2, frequency = 0.5,
                             amplitude = 20,
                             sensor_sd = 2.0)
# plot_trajectories(motiondata = motiondata)

@@

$$ \theta_t = \theta_{t-1} + \omega_{t-1} \Delta t + \alpha_{t-1} \frac{1}{2} \Delta t^2 $$
$$ \omega_{t} = \omega_{t-1} + \alpha_{t-1} \Delta t $$
$$ \alpha_t = \alpha_{t-1} $$

@@

$$ x_t = f(x_{t-1}, \epsilon) $$
$$ y_{t} = g(x_t, \delta) $$
$$ \epsilon \sim N(0, \sigma^2_\epsilon) $$
$$ \delta \sim N(0, \sigma^2_\delta) $$

<!-- TODO: it is better to start with the generative model, f() and g(), and then implement the state space description -->
where the state variable $x_t$ consists of the position $\theta_t$, velocity $\omega_t$ and acceleration $\alpha_t$, and $y_{t}$ denotes the sensory measurement.
<!-- [^sensormodel]  -->
$\epsilon$ and $\delta$ are zero-mean Gaussian noise terms with variances $\sigma^2_\epsilon$ and $\sigma^2_\delta$. These refer to the process and measurement noise, respectively. The process noise represents the uncertainty in the dependence of the current state on the previous state; under the constant velocity assumption, the process noise must be large enough if the model is to allow for change in velocity due to unmodelled acceleration. Note that the measurement noise is a model of the noise characteristics of the sensor, and not a physical property of the sensor itself. The function $f$ and $g$ represent the process transition function and the measurement function, respectively. 
<!-- In the case of a linear dynamical system, the transition function can be written as: -->
<!-- $$x_t \sim N(Ax_{t-1}), \epsilon^2)$$, -->
<!-- where the matrix $A$ replaces the transition function $f$. -->

@@

```{r 3d-statespace-fits, fig.cap="(a) Particle filter with a 3-d state space model for inferring velocity and position during a two-second head turn. (b) The same particle filter with increased process noise.", message=FALSE, warning=FALSE, include=FALSE}
cowplot::plot_grid(p_3d_1, p_3d_2, ncol = 2)
```
